\fontsize{10.5pt}{10.5pt}\selectfont
\begin{thebibliography}{2}

\bibitem{jour:NoC}
\newblock {Eduard Fernandez-Alonso, David Castells-Rufas, Jaume Joven and Jordi Carrabina}
\newblock {\emph{Survey of NoC and Programming Models Proposals for MPSOC}}
\newblock {IJCSI International Journal of Computer Science Issues, 2012, March, Vol.9. Issue 2, No.3

\bibitem{site:openshmem_spec}
\newblock {OpenSHMEM Specification v1.0 Final}
\newblock {http://openshmem.org/.}

\bibitem{site:shmem_api}
\newblock {SHMEM API for parallel programming}
\newblock {http://www.shmem.org/.}

\bibitem{site:intro_to_mpi}
\newblock {Introduction to MPI}
\newblock {http://www.citutor.org}

\bibitem{site:multicore_performance}
\newblock {Introduction to Multi-core Performance }
\newblock {http://www.citutor.org}

\bibitem{site:openmpi}
\newblock {Open MPI document v1.6.4}
\newblock {http://www.open-mpi.org/doc/}

\bibitem{jour:cci}
\newblock {Scott Atchley and David Dillow and Galen Shipman and Patrick Geoffray and Jeffrey M. Squyres and George Bosilca and Ronald Minnich}
\newblock {The Common Communication Interface ({CCI})}
\newblock {19th Annual IEEE Symposium on High-Performance Interconnects}
\newblock {(2011.08)}

\bibitem{jour:NIC}
\newblock {Keith D.Underwood, Michael J.Levenhagen, Ron Brightwell}
\newblock {Evaluating NIC Hardware Requirements to Achieve High Message Rate PGAS Support on Multi-Core Processors}
\newblock {ACM, SC07, 2007, November. pp. 10-16}

\bibitem{jour:programming_model}
\newblock {Henry Kasim, Verdi March, Rita Zhang, and Simon See}
\newblock {Survey on Parallel Programming Model}
\newblock {IFIP International Federation for Information Processing,(2008) . pp. 266-175}

\bibitem{jour:oneside}
\newblock {Christian Bell, Dan Donachea, Rajesh Nishtala, Ketherine Yelick}
\newblock {Optimizing Bandwidth Limited Problems Using One-Sided Communication and Overlap}
\newblock {IPDPS 2006. 20th International , (2006, April). pp.10 pp. 25-29}

\bibitem{jour:gshmem}
\newblock {Changil Yoon, Vikas Aggarval, Vrishali Hajare, Alan D.George, Max Billingsley III}
\newblock {GSHMEM: A Portable Library for Lightweight Shared-Memory Parallel Programming}
\newblock {\emph{PGAS'11}, (2011)}

\bibitem{jour:intra-node}
\newblock {Ron Brightwell, Kevin Pedretti}
\newblock {An Itra-Node Implementation of OpenSHMEM Using Virtual Address Space Mapping}
\newblock {\emph{PGAS '11}, (2011)}

\bibitem{jour:upc_on_tile}
\newblock {Olivier Serres, Ahman Anbar, Saumil Merchant and Tarek El-Ghazawi}
\newblock {Experiences with UPC on TILE-64 Processor}
\newblock {IEEEAero paper#1609, Version 2, (2010, December)}

\bibitem{jour:tshmem}
\newblock {Bryant C. Lam, Alan D. George, Herman Lam}
\newblock {TSHMEM: Shared-Memory Parallel Computing on Tilera Many-Core Processors}
\newblock {\emph{PGAS' 12}, (2012)}

\bibitem{book:computer_architecture}
\newblock {John L.Hennessy, David A.Patterson}
\newblock {Computer Architecture}
\newblock {Fifth Edition}
\newblock {USA: Morgan Kaufmann Publishers, Elsevier}
\newblock {(2012). pp. 344-426}

\bibitem{book:openmp}
\newblock {Barbara Chapman, Gabriele Jost, Ruud van der Pas}
\newblock {Using OpenMP, Portable Shared Memory Parallel Programming}
\newblock {USA: Massachusetts Institute of Technology
Publish}
\newblock {(2007). pp. 1-124}

\bibitem{book:chen}
\newblock {陈国良}
\newblock {并行算法的设计与分析}
\newblock {北京：高等教育出版社}
\newblock {2002.11}

\bibitem{book:intro}
\newblock {Peter Pacheco}
\newblock {An introduction to Parallel computing}
\newblock {USA: Morgan Kaufmann Publishers, Elsevier}
\newblock {(2011)}

\bibitem {book: para_arch}
\newblock {David Culler,Jaswinder Pal Singh, Anoop Gupta}
\newblock {USA: Morgan Kaufmann Publishers, Elsevier}
\newblock {(1997)}

\bibitem{book:encyclopedia_of_parallel_computing}
\newblock {Stephen W. Poole, Oscar Hernandez, Jeffery A. Kuehn, Galen M. Shipman, Anthony Curtis, and Karl Feind.}
\newblock {Encyclopedia of Parallel Computing, OpenSHMEM - Toward a Unified RMA Model}
\newblock {US: Springer, (2011).pp. 1379-1391}

\bibitem{book:encyclopedia}
\newblock {David Padua, etc.}
\newblock {Encyclopedia of Parallel Computing}
\newblock {US：Springer}
\newblock {(2011). pp. 1539-1544, pp.1812}

\bibitem{jour:hybrid}
\newblock Rabenseifner R, Hager G, Jost G. 
\newblock {Hybrid MPI/OpenMP parallel programming on clusters of multi-core SMP nodes[C]}
\newblock {Parallel, Distributed and Network-based Processing, 2009 17th Euromicro International Conference on. IEEE, (2009). pp. 427-436.}

\bibitem{book:sourcebook}
\newblock {Dongarra J J, Foster I, Fox G, et al.}
\newblock {Sourcebook of parallel computing[M].}
\newblock {San Francisco: Morgan Kaufmann Publishers, (2003)}

\bibitem{book:zhang}
\newblock {张林波, 并行计算导论[M], 清华大学出版社有限公司, 2006. pp.278-285}

\bibitem{book:pattern}
\newblock {McCool M, Reinders J, Robison A. Structured Parallel Programming: Patterns for Efficient Computation[M]. Morgan Kaufmann, 2012. pp.54-67}
\end{thebibliography}
